\documentclass[a4paper]{article}
    \usepackage{fullpage}
    \usepackage{amsmath}
    \usepackage{amssymb}
    \usepackage{textcomp}
    \usepackage[utf8]{inputenc}
    \usepackage{xparse}
    \usepackage{xstring}
    \usepackage{hyperref}
    \textheight=10in
    \pagestyle{empty}
    \raggedright

\include{lib/getenv.tex}

\hypersetup{
    colorlinks=true,
    urlcolor=black
}

\getenv[\gitsha]{GITHUB_SHA}

\setlength{\parskip}{1mm}

\newcommand{\hrefgithub} [1] {
    \href{https://github.com/#1}{github://#1}
}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

% DEFINITIONS FOR RESUME %%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\area} [2] {
    \vspace*{-9pt}
    \begin{verse}
        \textbf{#1}   #2
    \end{verse}
}

\newcommand{\lineunder} {
    \vspace*{-8pt} \\
    \hspace*{-18pt} \hrulefill \\
}

\newcommand{\header} [1] {
    {\hspace*{-18pt}\vspace*{6pt} \textsc{#1}}
    \vspace*{-6pt} \lineunder
}

\newcommand{\employer} [3] {
    { \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }
}

\newcommand{\contact} [3] {
    \vspace*{-10pt}
    \begin{center}
        {\Huge \scshape {#1}}\\
        #2 \\ #3
    \end{center}
    \vspace*{-8pt}
}

\newenvironment{achievements}{
    \begin{list}
        {$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}
    \end{list}
}

    % END RESUME DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%

    \begin{document}

\vspace*{-40pt}

%==== Profile ====%
\vspace*{-10pt}
\begin{center}
    {\Huge \scshape {Paul Chobert}}\\
    Software Engineer\\
    \ifx\empty\gitsha
    \else
        {\small resume version \href{https://github.com/barodeur/resume/tree/\gitsha}{\StrLeft{\gitsha}{7}}}\\
    \fi
    Montreal, QC, Canada $\cdot$ paul@chobert.fr $\cdot$ (438) 503 9004\\
    \hrefgithub{barodeur} $\cdot$ paulchobert.com
\end{center}

\vspace*{2mm}

%==== Profile summary ====%
\header{Profile summary}
\vspace{1mm}

\vspace{-1mm}
\begin{itemize} \itemsep 1pt
    \item 11 years profesional experience as a software engineer
    \item 4 years of experience as team leader
    \item Deep understanding of concurrent system design
    \item Strong DDD experience
    \item 11 years of experience with Ruby on Rails
    \item 6 years of experience with React \& 5 years with React Native
\end{itemize}
\vspace{-1mm}

%==== Experience ====%
\header{Experience}
\vspace{1mm}

\textbf{HOFr Sports} \hfill Remote\\
\textit{Full Stack Tech Lead} \hfill 2018 | 2021\\
\vspace{2mm}

HOFr is a daily fantasy sports app available in the US. For some years the application also operated as
a trivia application, having thousands on players in real time.

I was responsible for leading a small team of five developers to achieve a high-level of quality as well as
for outlining technical solutions early in the design process to make sure of their feasability.
I've been writing design documents about app features, epics and stories into our backlog.

I spent also a good amount of time reviewing submitted changes, making sure those correctly implements
the design, but also fit into out long term goals in term of tech debt management etc...

On a more technical aspect, I was usually responsible for achieving the most critical aspects of the application,
like the integration of payment processing. And also leveraging my 10 years experience with Rails and PostgreSQL
to prevent and fix performance related issues up to 20k req/s.

\vspace{2mm}
\raggedbottom

\textbf{QuickMail} \hfill Remote\\
\textit{Senior Software Engineer} \hfill 2017 | 2018\\
\vspace{2mm}

QuickMail is an email marketing software that let companies automate their Google Email accounts to send cold emails and followups.
We also perform reply detection to help our users filter their answers and manage their prospect list efficiently.

Since I joind I've been working with Jeremy the founder and our support team
to add features and maintain the existing codebase.
I've added feature like Microsoft Office 365 support while refactoring the existing
Rails MVC / Angular1.4 code into a nice and maintanable Rails / GraphQL / React codebase.

My role at QuickMail was also to take care of our large proxy infrastructure that let us avoid some spam detection.
I've automated the infrastructure using devops technique like using terraform and monitoring to setup and react quickly
to potential spam detection issue we might encounter.

\vspace{2mm}
\raggedbottom

\textbf{PAUL CHOBERT EURL} \hfill Worldwide\\
\textit{Founder \& Software Engineer} \hfill 2011 | Present\\
\vspace{2mm}

Founder and runs a solo consultancy business since 2011. Worked for many client, larges organisations like Unilever, SNCF (french national rails), and smaller startup.

Designed, developed, implemented, and maintained over twenty web and mobile applications.
The applications were in all kind of industries including vehicle tracking, Open Data, ticketing (online and onsite).

\vspace{2mm}
\raggedbottom

\textbf{Enternships | Startup} \hfill London, UK\\
\textit{Software Engineer - Lead developer} \hfill 2012 | 2013\\
\vspace{2mm}

\begin{itshape}
Enternships is a UK Job Board specialized into internships an placements.
They developped their own product as well as white labeled versions for business partners.
\end{itshape}

Replaced the leaving CTO of the company and took all responsabilities over maintenance within a week.

Refactored large legacy codebases to factorize web applications together.
The products were functionally similar but had completly independant codebase.

Recruited two junior developpers and lead the team to achieve a faster development cycle.

\vspace{2mm}
\raggedbottom

\textbf{Extessy | Volkswagen Enginneering Company} \hfill VW Town | Wolfsburg, Germany\\
\textit{Software Engineer Intern} \hfill Summer 2008\\
\vspace{2mm}

\begin{itshape}
Extessy AG, now part of Accenture was a software engineering firm providing integration tools for software components at Volkswagen.
\end{itshape}

Designed and implemented a solution to convert poorly structured MS Word documents into Requirements Interchange Format documents.

Learned parser design to implement advanced conversion tools.

Learned UML2 Class Diagrams to document the solution.

\vspace{2mm}
\raggedbottom

\header{Technical strenght}
\begin{tabular}{ l l }
    Programming Languages:  & Ruby, Javascript, Golang, Exlir, Scala, Java, Bash   \\
    Databases:              & Postgresql, Elasticsearch, MongoDB, DynamoDB  \\
    Web stacks:             & Ruby on Rails, Node.js, React                        \\
    Infrastructure:         & AWS, Docker, Kubernetes, Terraform, Chef             \\
\end{tabular}

\header{Projects}
{\textbf{Personal Kube Cluster} \sl 2021 | SIDE PROJECT | Kubernetes, Terraform} \hfill \hrefgithub{chobert/kube}\\
Since 2021 I've been operating a personal \& educational kubernetes cluster to host a couple of services for my family.
I've deployed an authentication service at id.chobert.fr (keycloack), as well as a couple of other services
relying on the authentication service. Those include a matrix server (matrix.chobert.fr),
and gitlab instance (gitlab.chobert.fr)
\vspace*{2mm}

{\textbf{Chobchat} \sl 2021 | SIDE PROJECT | React Native, Rescript, Electron} \hfill \hrefgithub{barodeur/chobchat}\\
Chobchat is a simplified version of a matrix client that is targetted for kids.
Instead of having my 4yo nefew on facebook messenger, or google, I've deployed a matrix.org server on the family kube cluster
and created a simplified matrix client for his Raspberry Pi 400.
The application is a universal React app, working on web, iOS, Android, linux, and macOS.
The CD produces builds on every git tag and the desktop clients automatically updates itself.
\vspace*{2mm}

{\textbf{React Native NFC iOS} \sl 2017 | SIDE PROJECT | react} \hfill \hrefgithub{barodeur/react-native-nfc-ios}\\
An open source library to use Apple CoreNFC with React Native.
\vspace*{2mm}

{\textbf{MesVaccins Pro Mobile} \sl 2017 | CLIENT PROJECT | react native} \hfill Currently in Beta\\
\begin{itshape}
MesVaccins is a leading solution in the vaccination industry.
Their flexible expert system is trained withthousands of vaccinations rules.
\end{itshape}

\vspace{-\topsep}
\begin{itemize}
    \item Designed a mobile application by following iOS and Google design principles
\end{itemize}
\vspace{-\topsep}

\vspace*{2mm}

{\textbf{Vote\&Vous App} \sl 2016 | CLIENT PROJECT | node.js, react, serverless, dynamodb} \hfill app.vote-et-vous.fr\\
I designed and developed a tool to help electors choose the closest candidate to their ideas.
I used a serverless infrastructure to handle traffic peaks coming from our embeded widget on media partners.
\vspace*{2mm}

{\textbf{Ice Rink Ticket System} \sl 2016 | CLIENT PROJECT | node.js, postgresql} \hfill Private\\
That Group LTD is operating a few paid ice rinks in the UK during the christmas season.
I developed a full online ticketing solution and an on-site boxoffice connected to a receipt printer and cash drawer.
\vspace*{2mm}

{\textbf{Anoloc} \sl 2015 | CLIENT PROJECT | nodejs, angular} \hfill www.anoloc.fr\\
I helped maintain and add features to their vehicle tracking platform.
The main challenge was to identify scalability issues and fix them.
Most of those were solved by distributing tasks to a worker pool.\\
\vspace*{2mm}

{\textbf{Teltonica support for Anoloc} \sl 2015 | CLIENT PROJECT | IoT, golang} \hfill www.anoloc.fr\\
Anoloc was about to use a new tracking hardware on vehicles.
I implemented the server to receive UDP frames for the new Teltonika protocol.
\vspace*{2mm}

{\textbf{Makesense, Future of Waste, Ecowork} \sl 2014 | CLIENT PROJECT | rails} \hfill\\
I maintained a Ruby on Rails platform for the Makesense project and helped terminate a project that was functionally similar.
Later, for a thrid project I factorized the many duplications of those three platforms into a Rails Engine in order
to accelerate the development of new white labels.
\vspace*{2mm}

{\textbf{Ray Ban Sales traning for Luxottica} \sl 2013 | CLIENT PROJECT | javascript, moodle} \hfill Private\\
I developed a Moodle class to train Ray Ban sellers with the marketing materials from Luxottica.
The module was a javascript interface where the learner would watch videos and take tests.
Test results were sent to Moodle to generate tracking and statistics data.\\
\vspace*{2mm}

{\textbf{SNCF Open Data} \sl 2012 | CLIENT PROJECT | rails} \hfill data.sncf.com\\
I was chosen to develop the Open Data platform of the French national rails company SNCF.
The app was online from 2012 to 2017 but was later replaced with a SaaS product.
My work is archived on archive.org\\
\vspace*{2mm}

{\textbf{Unilever Sustainable Living Lab} \sl 2012 | CLIENT PROJECT | rails, emberjs} \hfill Private\\
I helped a team at Tquila London (now Accenture) to customise a Discourse forum for Unilever needs.
This was challenging as Ember \& Discourse were not stable at the time. \\
I was also in charge of maintaining a second hosting solution in case we had any problems with Heroku EU zone (also beta).
My solution was a Chef managed cluster of Linodes.\\
\vspace*{2mm}


{\textbf{Voxe.org} \sl 2011 | CLIENT PROJECT | rails} \hfill www.voxe.org\\
I worked with Pierre Valade to develop a tool to compare political programs for the French Presidential election of 2012.
The app was a massive success and brought me visibility to later continue my freelance career.\\
\vspace*{2mm}

{\textbf{Wisemetrics} \sl 2011 | CLIENT PROJECT | rails, mongodb} \hfill www.wiselytics.com\\
I developed an advanced Facebook analytics platform to help content managers reach their audiences.
This was when Facebook didn't have a GUI to see this data, but most of them were available through the API (FQL).
The product was later sold and became Wiselytics.\\
\vspace*{2mm}

%==== Education ====%
\header{Education}
\vspace{1mm}

\textbf{Master of Science in Engineering}\hfill Strasbourg, France\\
École Nationale Supérieure d'Informatique pour l'Industrie et l'Entreprise - ENSIIE\hfill Grad: 2013\\
\vspace{2mm}
\textbf{BSc Physics - ENSPS}\hfill Strasbourg, France\\
Télécom Physique Strasbourg\hfill Grad: 2011\\
\vspace{2mm}

\vspace*{2mm}

\ 
\end{document}
